brados: declarative, programmable object storage

### 2016-05-24 paper.tex
paper: update fig
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
paper: udpate
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\title{outline!}

\author{
%Noah Watkins, Neha Ojha\textsuperscript{*}, Carlos Maltzahn \\
%\small {\em University of California, Santa Cruz} \\
%\small {\{jayhawk,carlosm\}@cs.ucsc.edu} \textsuperscript{*}nojha@ucsc.edu \\ [2mm]
\small Submission Type: Research
}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{.48\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{figures/ceph}
      \caption{Ceph}
      \label{fig:ceph}
  \end{subfigure}\quad
  \begin{subfigure}[b]{.40\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{figures/osd}
      \caption{OSD}
      \label{fig:osd}
  \end{subfigure}
  \caption{Ceph and OSD... gotta cram more stuff in here...}
\end{figure}

@@

\section{Programming Model}

Ceph is turning into a target for building distrubted services, bringing
distributed programming into the hands of many new people that may have
worked on the periphery of ceph.

Getting consistency and coordination correct is a challenge And as we have seen
optimization at a low-level given a simple set of semantics can yield a large
state space from which to draw designs Difficulty and challenges of writing
distributed software.  Programming distributed systems and applications.

We draw upon the recent work of Bloom a declarative lang thing

BLL (a.k.a. BRADOS) is a declarative language with relational (or tabular)
semantics for RADOS objects, which corresponds to a subset of the BLOOM
language (leaving out temporal logic). BLL borrows from BLOOM the table and
interface collections, the instantaneous implication (‘<=’) operator, as well
as all the collection operators.

BRADOS models the storage system state uniformly as a collection of relations.
The composition of a collection of existing interfaces is then expressed as a
collection of high-level \emph{queries} that describe how a stream of requests
(API calls) are filtered, transformed and combined with existing state to
define streams of outputs (API call returns as well as updates to system
state).  Separating the relational semantics of such compositions from details
of their physical implementations introduces a number of degrees of freedom,
similar to the ``data independence’’ offered by database query languages.  The
choice of access methods (for example, whether to use a bytestream interface or
a key/value store), storage decide classes(e.g., whether to use HDDs or SDDs),
physical layout details (e.g. a 1:1 or 1:N mapping) and execution plans (e.g.
operator ordering) can be postponed to execution time.  The optimal choices for
these physical design details are likely to change much more often than the
logical specification, freeing the interface designer from the need to rewrite
systems and device and interface characteristics change.

\subsection{The CORFU Interface in Bloom}

>>>>

\title{brados: declarative, programmable object storage}

\author{
Noah Watkins, Michael Sevilla, Ivo Jimenez, \\Neha Ojha, Peter Alvaro, Carlos
Maltzahn\\
\small {\em University of California, Santa Cruz} \\
%\small {\{jayhawk,carlosm\}@cs.ucsc.edu} \textsuperscript{*}nojha@ucsc.edu \\ [2mm]
\small Submission Type: Research
}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{.48\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{figures/ceph}
      \caption{Ceph Cluster}
      \label{fig:ceph}
  \end{subfigure}\quad
  \begin{subfigure}[b]{.40\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{figures/osd}
      \caption{OSD Arch}
      \label{fig:osd}
  \end{subfigure}
  \caption{The Ceph cluster is composed of object storage devices (OSD) that
  support object transactions and a rich set of hardware and software
configurations.}
\end{figure}

@@

\section{The Brados Programming Model}

As Ceph continues to develop into a target for building distributed services
and application, it is important to not restrict use to developers seasonsed
in distributed programming and those with knowledge of intracacies of the Ceph
performance model.  To this end we present Brados, a declarative language with
relational semantics for defining the behavior of RADOS object interfaces.

The Brados model corresponds to a subset of the Bloom language, and models the
storage system state uniformly as a collection of
relations~\cite{alvaro:cidr11}. The composition of a collection of existing
interfaces is then expressed as a collection of high-level \emph{queries} that
describe how a stream of requests (API calls) are filtered, transformed and
combined with existing state to define streams of outputs (API call returns as
well as updates to system state).  Separating the relational semantics of such
compositions from details of their physical implementations introduces a
number of degrees of freedom, similar to the ``data independence’’ offered by
database query languages.  The choice of access methods (for example, whether
to use a bytestream interface or a key/value store), storage decide
classes(e.g., whether to use HDDs or SDDs), physical layout details (e.g. a
1:1 or 1:N mapping) and execution plans (e.g.  operator ordering) can be
postponed to execution time.  The optimal choices for these physical design
details are likely to change much more often than the logical specification,
freeing the interface designer from the need to rewrite systems and device and
interface characteristics change.

\subsection{Basics}

\subsection{The CORFU Log Interface}
